Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-08-03 draft_lm1.tex
finished the incomplete paragraph. closes #45

Dengue has been reintroduced in Rio de Janeiro in 1986 after being absent for 
68 years~\citep{nogueira1999dengue}.
During the last decades of the 20th century only DEN-1 and DEN-2 serotypes

>>>>

Dengue has been reintroduced in Rio de Janeiro in 1986 after being absent for 
68 years~\citep{nogueira1999dengue}.
During the last decades of the 20th century only DEN-1 and DEN-2 serotypes were 
in circulation. The remaining serotypes DEN-3 and DEN-4, arrived respectively 
in 2000 and 2011 \citep{de2004dengue, nogueira2011dengue}. Due to this patterns 
of recent re-introduction of the disease, its incidence dynamics is still 
dominated by the introduction events and environmental determinants of 
transmission.
